A Bayesian ranking statistic to find high-mass black holes in LIGO--Virgo data

### 2021-03-15 main.tex

%%%%%%---SECTIONS---%%%%%%%%%%%%
\section{New Intro}
In the 1960s, X-ray and optical observations from the Cyg-X1 binary star system led to the discovery of the first stellar-mass black hole~\cite{}. Shortly afterwards, in 1974, kinematic measurements of stars near the center of our galaxy demonstrated the presence of a supermassive black hole of mass $10^6\ \text{M}_{\odot}$ -- Sag A$^*$~\cite{}. These two detections firmly established the existence of stellar-mass
black holes $\text{M}_\text{BH} < 10^{2} \ \text{M}_{\odot}$ and
supermassive black holes, $\text{M}_\text{BH} > 10^{5} \ \text{M}_{\odot}$ in our universe. Since then, astronomers accumulated more definitive evidence for stellar-mass and supermassive black holes. However, a gap in between the mass-ranges of these two categories began to form: there is a deficiency of black holes in the intermediate-mass range $10^{2} - 10^{5}\ \text{M}_{\odot}$. These intermediate-mass black holes must have existed to form the supermassive black holes detected to exist in the early universe~\cite{}. However, we only have a handful of candidates and one confirmed intermediate-mass black hole~\cite{}. The study and discovery of intermediate-mass black holes will help bridge the gap and provide a pathway to forming supermassive black holes.

Intermediate-mass black holes may form various scenarios ranging from hierarchical mergers of stellar-mass black holes to large metal-free stars' direct collapse. Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible method for black holes to accumulate mass and reach the intermediate-mass range. However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s. Hence, the merger remnants require their recoil kick to be less than its environment's escape velocity to undergo successive mergers. This tight constraint makes hierarchical mergers a challenging scenario.

Another pathway to form intermediate-mass black involves the direct collapse of massive, metal-free Population III stars. Typically, massive stars $> 100 \ \msun$ can eject more than half of their mass in the form of radiatively driven stellar winds. However, at zero metallicity, mass loss through stellar winds is negligible (Kudritzki 2000). Hence,  Population III stars have the opportunity to complete their life-cycles without losing a significant portion of their mass. Moreover, Population III stars with masses above $230 \ \msun$ will avoid electron-positron pair-instability. Consequently, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependant on the initial star mass (Bond et al. 1984). The intermediate-mass black holes that form as remnants of these large Population III stars may exist today in clusters located at the galaxies' bulges. If these bulges contain intermediate-mass black holes, they could also provide evidence for Population III stars' existence.

As there is inadequate observational evidence for intermediate-mass black holes, it is challenging to state which formation path is favoured. However, the observational work does allude to the existence of intermediate-mass black holes. The search for intermediate-mass black holes is underway using direct kinematic measurements, reverberation mapping, studying luminosity from low-luminous active galactic nuclei and Ultraluminous X-ray Sources.

Dynamic measurements of individual sources orbiting an intermediate-mass black hole is that the sphere of influence too small to resolve motions. Can only be used on close sources. The issue with reverberation mapping and the other EM spectra, cant be sure of anisotropic emission, non-linear emission. large uncertainties. \url{https://iopscience.iop.org/article/10.3847/2041-8213/ab745b}

The most promising avenues to find $100-1000 Msun$ black holes are either to identify stellar binaries, which are expected to be common or to detect them in gravitational radiation. Ground based gravitational-wave limits on the low end of this mass regime are continuing to improve.

LIGO found 190521, can find more if we are more sensitive, and if we can better harness data

\section{\label{sec:Introduction}Introduction}

Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes. In April 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87~\cite{m87photo}. As of January 2021, the LIGO Scientific Collaboration has confirmed $\sim50$ binary black hole systems and listed numerous candidate events~\cite{GWTC1, GWTC2, gracedb}. Additionally, since the public release of LIGO's first and second observing run's data (O1 and O2), search pipelines such as \pycbc~\cite{pycbc_code} and a research team at the Institute for Advanced Study (IAS)~\cite{IAS0, IAS1, IAS2}, have independently identified additional binary black hole gravitational-wave candidates.

\et{Add a paragraph here discussing basic ideas in IMBH theory. Explain why the are not easy to make. Discuss scenarios by which they can be made. Discuss the role they may play in the formation of supermassive BH. Then, we transition to the next paragraph about observational evidence.}

Until recently, there was no definitive evidence for intermediate-mass black holes with a mass in between the range of stellar-mass and supermassive black holes ($10^2-10^6\ \msun$). 
\et{There have been numerous claims of IMBH detection. The previous sentence is correct that there are no \textit{definitive} detections before GW190521, but the paragraph is misleading by omission. Insert here an exhaustive review of previous IMBH detection claims, noting who made the claim, the mass, and the method.}
This changed with the detection of GW190521, a unique gravitational-wave event that led to the formation of a black hole with a mass  $142\ \msun$, the first confirmed direct discovery of an intermediate-mass black hole~\cite{gw190521}. Although this is the first gravitational-wave observation of an IMBH, ground-based gravitational-wave detectors are sensitive to gravitational-waves from even more massive systems with a total mass of up to $400\ \msun$~\cite{GWTC1}.

\et{The following paragraph tries to solve a problem that doesn't exist: as noted in comments above, the absence of GWs from IMBH is not surprising. Delete or rewrite if you want to emphasise the difficulty in IMBH detection.}
A possible explanation for the absence of intermediate-mass events may be due to their misclassification as short-duration instrumental noise transients known as glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational-wave events.

One method to account for glitches while searching for gravitational-waves from coalescing compact binaries (CBCs) is by utilising the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}. A true Bayesian odds, calculated without using bootstrap techniques, can provide more accurate estimate of significance that does note depend on the search pipeline~\cite{BCR2, bcr_gw151216,  bayesian_odds}.
In this paper, we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational-wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2. Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds, it provides a more astrophysical measure of candidate events' significance than a traditional match-filter significance.
\et{This pitch, that the method is ``a more astrophysical measure'' is unconvincing. (What does that even mean?) Chat with RS/ET to come up with a better pitch built around the idea that the detection statistic is built on Bayesian inferences results, and that it's a step toward fully Bayesian detection.}

@@

\subsection{Calculating the Significance of Candidates}
Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis). A false alarm probability with trial factors, \fap, for the candidate \bcr-values can quantify the significance. The \fap is the probability that a candidate originating from a non-astrophysical source can be is falsely identified as a signal.

To calculate the \fap, each candidate \bcr is considered a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background \bcr greater than or equal to the candidate \bcr,
\begin{equation}
    f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
\end{equation}
The false alarm probability with trails \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate triggers is
\begin{equation}
    \fap = 1 - (1-f)^N \ .
\end{equation}

@@

\caption[BBH parameters corresponding to duration $<454\ \text{ms}$]{\label{tab:parameters}High-mass parameter space (parameters corresponding to signals with durations $<454 \ \text{ms}$). }
\centering
\begin{tabular}{lrr}
\toprule
  & Minimum & Maximum\\
\midrule
Component Mass 1 [\msun] & 31.54 & 491.68\\
Component Mass 2 [\msun] & 1.32 & 121.01\\
Total Mass [\msun] & 56.93 & 496.72\\
Chirp Mass [\msun] & 8.00 & 174.56\\
Mass Ratio & 0.01 & 0.98\\
\end{tabular}
\end{table}

@@

\subsection{Calculating the BCR for triggers}
To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler. Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.

@@

\begin{table}
    \centering
    \caption{
    Prior settings for the parameters used during our parameter estimation. The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.\label{tab:priors}}
    \begin{tabular}{c c c c}
    \hline
    Parameter & Shape & Limits & Boundary \\
    \hline
          $\mathcal{M}/\msun$           & Uniform & 7--180 & Reflective \\
          $q$                           & Uniform & 0.1--1 & Reflective \\
          $M/\msun$                     & Constraint & 50--500 & -- \\
          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000 & Reflective \\
          $a_1$, $a_2$                  & Uniform & 0--1 & Reflective \\
          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$ &  Reflective \\
          $\psi$                        & Uniform & 0--$\pi$ &  Periodic \\
          $\phi$                        & Uniform & 0--$2\pi$ &  Periodic \\
          ra                            & Uniform & 0--$2\pi$ &  Periodic \\
          dec                           & Cosine & 0--$2\pi$ &  Reflective \\
    \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[!ht]
{\centering \includegraphics[width=0.75\linewidth]{images/bcr_cdf_smaller_legend.png} }
\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (grey) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$. Vertical lines mark the $\text{ln}\ \bcr$ of IAS's GW170817 and GWTC-1's GW170814.}\label{fig:bcrCdf}
\end{figure}

@@

\section{Bayesian Evidence Evaluation}
\subsection{Noise Model}
\rs{I suggest moving this subsection to an appendix}
We assume that each detector's noise is Gaussian and stationary over the period being analysed~\cite{ligo_psd}. In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data. Using the \psd, for each data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write 
\begin{equation}
\label{eq:zn}
Z^N_i = \mathcal{N}(d_i) = \frac{1}{2\pi \psd_i} \ \text{exp}\left(-\frac{1}{2} \frac{d_i}{\psd_i} \right) \ ,
\end{equation}
where $\mathcal{N}(d_i)$ is a normal distribution with $\mu=0$ and $\sigma^2\sim \psd$.

@@

O2 lasted several months over which the detector's sensitivity varied. Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $\alpha$ and $\beta$, as described in Section~\ref{sec:method}. Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilised for each time-frame of O2 data. \avi{note: havent tuned all chunks yet -- and tbh the 'tuning' could be better, atm brute force searching a 2d log-spce grid}
\input{Data/alpha_beta_table}

>>>>

%%%%%%---SECTIONS---%%%%%%%%%%%%
\section{Introduction}
In the 1960s, X-ray and optical observations from the Cyg-X1 binary star system led to the discovery of the first stellar-mass black hole~\cite{}. Shortly afterwards, in 1974, kinematic measurements of stars near the center of our galaxy demonstrated the presence of a supermassive black hole of mass $10^6\ \msun$ -- Sag A$^*$~\cite{}. These two detections firmly established the existence of stellar-mass
black holes $\text{M}_\text{BH} < 10^{2} \ \msun$ and
supermassive black holes, $\text{M}_\text{BH} > 10^{5} \ \msun$ in our universe. Since then, astronomers accumulated more definitive evidence for stellar-mass and supermassive black holes. However, a gap in between the mass-ranges of these two categories began to form: there is a deficiency of black holes in the intermediate-mass range $10^{2} - 10^{5}\ \text{M}_{\odot}$. These intermediate-mass black holes must have existed to form the supermassive black holes detected to exist in the early universe~\cite{}. However, we only have a handful of candidates and one confirmed intermediate-mass black hole~\cite{}. The study and discovery of intermediate-mass black holes will help bridge the gap and provide a pathway to forming supermassive black holes.

The two main proposed formation channels for Intermediate-mass black holes are the light-seed and the heavy-seed channels. The light-seed channel involves dynamic interactions of low-mass seeds, e.g. hierarchical mergers of stellar-mass black holes, runaway collisions of stars.  The heavy-seed channel involves the direct collapse of high-mass seeds, e.g. the direct collapse of giant metal-free Population III stars or early protogalaxies' collapse.  Although promising pathways, there are challenging obstacles both scenarios must overcome to pathways that can form intermediate-mass black holes.

Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible light-seed method for black holes to accumulate mass and reach the intermediate-mass range. However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s. Hence, the merger remnants require their recoil kick to be less than its environment's escape velocity to undergo successive mergers. This tight constraint makes hierarchical mergers a challenging scenario. One proposed heave-seed pathway involves the direct collapse of massive, metal-free Population III stars. Typically, massive stars $> 100 \ \msun$ can eject more than half of their mass in the form of radiatively driven stellar winds. However, at zero metallicity, mass loss through stellar winds is negligible \cite{Kudritzki 2000}. Hence,  Population III stars have the opportunity to complete their life-cycles without losing a significant portion of their mass. Moreover, Population III stars with masses above $230 \ \msun$ will avoid electron-positron pair-instability. Consequently, oxygen and silicon burning will not drive an explosion, allowing the star to undergo a complete collapse to leave behind an intermediate-mass black hole remnant with a mass of $120-280 \ \msun$, dependant on the initial star mass \cite{Bond et al. 1984}. Hence, the formation of intermediate-mass black holes from Population III stars is directly proportional to the fraction of Population III stars with masses above $230 \ \msun$, a fraction that is still uncertain~\cite{Coleman Miller, Formation Scenarios for Intermediate-Mass Black Holes}.

% - Bridge between light-seed and heavy-seed formation and observation
% - Although IMBH gap isnt completly filled, observational work conducted in the past 20 years points to the existence of intermediate-mass black holes .

% - To prove the existence of IMBH we need to measure their BH's masses
% - We can measure mass by two main methods: direct kinematic, emission (reverberation mapping, luminosity, gw)
% - Discuss Candidates
% - LIGO a good way. 190521g uncertain
% - Challenges of IMBH from ground-based
% - THUS We need a better way to discriminate between glitches and high-mass signals -- BCR!

To prove the existence of intermediate-mass black holes, the scientific community needs to measure the mass of a black hole inside the IMBH range. However, measuring the mass of black holes can be challenging.

It is possible to measure the mass of nearby supermassive black holes (such as Sag A) by directly observing the dynamic motion of stars nearby the supermassive black hole. However, this dynamic measurement method is challenging to utilise for IMBHs as their sphere of influence is too small to resolve motions. Additionally, dynamic-measurements that have alluded to IMBH candidates, e.g. the candidate at the centre of the globular cluster 47 Tucanae \cite{kiziltan 2017}, can also be attributed to simpler models without a central IMBH \cite{freire 2017}.

In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes  \cite{Ferrarese & Merritt 2000 and Gebhardt et al. 2000}, it cannot accurately estimate the mass of IMBHs. The M-$\sigma$ and M-L relations are not calibrated for low-mass galaxies that might host an IMBH as its central black hole \cite{J. E. Greene and L. C. Ho The Mass Function of Active Black Holes in the Local Universe, E. C. Moran, K. Shahinyan, H. R. Sugarman, D. O. Vélez and M. Eracleous Black Holes At the Centers of Nearby Dwarf Galaxies}. Table 2 of ~\citet{mercuza} displays a list of IMBH candidates found with these relations.

Another method to estimate large black hole masses is reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities \cite{reverberation mapping}. Reverberation mapping has shown to estimate both supermassive black hole and IMBH virial masses successfully. However, this method fails to measure the systematic uncertainties on the low-mass IMBH masses ~\cite{}. Additionally, cloud-variability and the possibility of anisotropic emission deride the credibility of IMBH candidates found with reverberation mapping.

The most promising IMBH candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources (with luminosities $> 10^{39} \text{erg s}^{-1}$). While stellar mass black holes are too small to generate such luminosities with Eddington accretion, Intermediate mass black holes can accrete at rates large enough to account for the high luminosities \cite{}. The drawback to this approach is the assumption that super-Eddington accretion is impossible and that X-ray emission from the sources is isotropic.

Finally, another channel to measure BH masses is from gravitational waves. Identifying GW from mergers of compact binaries. Ground-based gravitational-wave limits on the low end of this mass regime are continuing to improve. LIGO found 190521, can find more if we are more sensitive, and can better harness data.

IMBH hard to find as very similar to short-duration instrumental noise transients known as glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. These glitches can mimic astrophysical signals and hence decrease the significance of true gravitational-wave events.

One method to account for glitches while searching for gravitational-waves from coalescing compact binaries (CBCs) is by utilising the astrophysical Bayesian odds~\cite{bci, BCR1, BCR2, bcr_gw151216, bayesian_odds}. A true Bayesian odds, calculated without using bootstrap techniques, can provide more accurate estimate of significance that does note depend on the search pipeline~\cite{BCR2, bcr_gw151216,  bayesian_odds}.
In this paper, we utilise a Bayesian method, called the Bayesian Coherence Ratio \bcr~\cite{BCR1}, to rank the candidate gravitational-wave signals from high-mass compact binary coalescences (systems with total masses in the range of $55-500\ \msun$) in the detector data recorded during O2. Although the \bcr, utilising bootstrap techniques, does not provide the true Bayesian odds,  it utilizes Bayesian evidences which describe the explicit probability of data under the hypothesis that it contains coherent signals vs incoherent glitches.

@@

\subsection{Calculating the Significance of Candidates}
Candidate \bcr-values are either statistically insignificant compared to the background \bcr distribution, implying the candidate is more probable to be an incoherent instrumental feature (the $\mathcal{H}_I$ null-hypothesis), or statistically significant to the background distribution, indicating the possible presence of an astrophysical signal (the $\mathcal{H}_S$ hypothesis). A false alarm probability with trial factors, \fap, for the candidate \bcr-value can quantify the significance. The \fap is the probability that a candidate originating from a non-astrophysical source can be is falsely identified as a signal.

To calculate the \fap, each candidate \bcr is considered a single statistical trail that can occur at a fixed false alarm probability $f$, where $f$ is the probability of observing a background $\bcr'$ greater than or equal to the candidate \bcr,
\begin{equation}
    f = \frac{\text{Count of } \bcr' \leq \bcr}{\text{Count of } \bcr'} \ .
\end{equation}
The false alarm probability with trails \fap that the \bcr measurement occurs at least once for $N$ trials $(N > 0)$, where $N$ is the number of candidate triggers is
\begin{equation}
    \fap = 1 - (1-f)^N \ .
\end{equation}

@@

\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}High-mass parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
\centering
\begin{tabular}{lrr}
\toprule
  & Minimum & Maximum\\
\midrule
Component Mass 1 [\msun] & 31.54 & 491.68\\
Component Mass 2 [\msun] & 1.32 & 121.01\\
Total Mass [\msun] & 56.93 & 496.72\\
Chirp Mass [\msun] & 8.00 & 174.56\\
Mass Ratio & 0.01 & 0.98\\
\end{tabular}
\end{table}

@@

\subsection{Calculating the BCR for triggers}
\avi{Sat 13th: Just realised that some parts of this dont make sense without the material present in Apdx~\ref{sec:bayesianEvidEval}}...
To evaluate $Z^S$, $Z^G_i$ and $Z^N_i$ and calculate the \bcr Eq.~\ref{eq:bcr} for triggers, we carry out Bayesian inference with \bilby~\cite{bilby, bilby_pipe}, employing \dynesty~\cite{dynesty} as our nested sampler. Nested sampling, an algorithm introduced by~\citet{skilling2004, skilling2006}, provides an estimate of the true Bayesian evidence and is often utilised for parameter estimation within the LIGO collaboration~\cite{bilby, bilby_paper, pbilby_paper}.

@@

\begin{table}
    \centering
    \caption{
    Prior settings for the parameters used during our parameter estimation. The definitions of the parameters are documented in \citet{bilby_gwtc}~Table~E1.\label{tab:priors}}
    \begin{tabular}{c c c c}
    \hline
    Parameter & Shape & Limits \\
    \hline
          $\mathcal{M}/\msun$           & Uniform & 7--180  \\
          $q$                           & Uniform & 0.1--1  \\
          $M/\msun$                     & Constraint & 50--500  \\
          $d_\mathrm{L}/\mathrm{Mpc}$   & Comoving & 100--5000  \\
          $a_1$, $a_2$                  & Uniform & 0--1  \\
          $\theta_{JN}$                 & Sinusoidal & 0--$\pi$  \\
          $\psi$                        & Uniform & 0--$\pi$  \\
          $\phi$                        & Uniform & 0--$2\pi$  \\
          ra                            & Uniform & 0--$2\pi$  \\
          dec                           & Cosine & 0--$2\pi$  \\
    \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[!ht]
{\centering \includegraphics[width=0.85\linewidth]{images/bcr_cdf_smaller_legend.png} }
\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (grey) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$. Vertical lines mark the $\text{ln}\ \bcr$ of IAS's GW170817 and GWTC-1's GW170814.}\label{fig:bcrCdf}
\end{figure}

@@

\section{Bayesian Evidence Evaluation}\label{sec:bayesianEvidEval}
\subsection{Noise Model}
We assume that each detector's noise is Gaussian and stationary over the period being analysed~\cite{ligo_psd}. In practice, we assume that the noise has a mean of zero that the noise variance $\sigma^2$ is proportional to the noise power spectral density (PSD) \psd of the data. Using the \psd, for each data segment $d_i$ in each of the $i$ detectors in a network of $D$ detectors, we can write 
\begin{equation}
\label{eq:zn}
Z^N_i = \mathcal{N}(d_i) = \frac{1}{2\pi \psd_i} \ \text{exp}\left(-\frac{1}{2} \frac{d_i}{\psd_i} \right) \ ,
\end{equation}
where $\mathcal{N}(d_i)$ is a normal distribution with $\mu=0$ and $\sigma^2\sim \psd$.

@@

O2 lasted several months over which the detector's sensitivity varied. Hence, a part of our analysis entailed tuning the prior odds for obtaining a signal and a glitch, $\alpha$ and $\beta$, as described in Section~\ref{sec:method}. Table~\ref{tab:priorodds} presents the signal and glitch prior odds utilised for each time-frame of O2 data. 
\input{Data/alpha_beta_table}
